Epistemic Semantics in Guarded String Models\thanks{Thanks guys.}

### 2021-01-15 tex/pdraft.tex
fix typo
Substitute for (12) plus changes to end of Section 6.

\newcommand{\HEADS}{\bullet^*h}
\newcommand{\AKWH}{\neg (\neg \HEADS \vee \Diamond_{a} \neg\HEADS) + \neg(\HEADS \wedge \Diamond_{a}\HEADS)}
\newcommand{\BKAKWH}{\neg(\neg(\AKWH) + \Diamond_{b}\neg(\AKWH))}
\newcommand{\AKBKAKWH}{\neg(\neg(\BKAKWH) + \Diamond_{a}\neg(\BKAKWH))}

\begin{examples} \label{three}
\itema It's tails and Amy knows that Bob knows that Amy knows whether it's heads.
% (_*;t) & ~ <amy> ~ ~ <bob> ~((~ (<amy> ~ (_*;h))) + ~ (<amy> (_*;h)) )
\itemb \( \displaystyle \bullet^*t \wedge \AKBKAKWH \)
\itemc \(\bullet^*t \wedge \K_{a}(\K_{b}(\K_{a} \bullet^* h + \K_{a} \neg \bullet ^* h))\)
\itemd Amy knows that it's tails.
\iteme \(
\bullet ^*t \wedge \neg \Diamond_{a} \neg \bullet^*t~~~~~~(\equiv \K_a \bullet^* t)
\)

\end{examples}

Sentence \exi{three}{d} is assigned the logical form \exi{three}{e} by
the grammar.  Logical relations between propositions are checked in
the finite state calculus by checking set-theoretic relations between
sets of worlds.  For instance entailment $p \rightarrow q$ is decided
by checking in an interpreter for the finite state calculus whether $p
- q$ is non-empty.  In the model defined by Figure 2, the propositions
\exi{three}{b} and \exi{three}{e} are independent. They are equivalent
in a version without secret flipping.

%% \begin{examples} \label{entail}
%% \itema Amy knows that it's tails.
%% \itemb \(
%% \neg \Diamond_{a} \neg \bullet^*t
%% \)
%% % \itemc \(\displaystyle \Box_{a}\Box_{b}(\Box_{a} \neg \bullet^* h + \Box_{a}\neg \bullet^* t)\) \hfill \mbox{} \(~~\cdot~~\Box_{a}\neg\Box_{b}\Box_{a}\neg \bullet^* t\)
%% \end{examples}

\section{Discussion}
Epi\textsc{Kat} is designed for use in linguistic semantics research, for
computational linguistics research on model-theoretically grounded semantics,
and for students in graduate course modules on intensional formal semantics.
Currently, the grammar covers statives, {\em that-} and {\em
  whether}-complements, negation, and predicate and sentence conjunction.

There are straightforward extensions to additional linguistic phenomena, such as
tense and perfective aspect \exi{extension}{a}, and the combination of
metaphysical modality and prospective aspect \exi{extension}{b}.

@@

\clearpage

>>>>

\newcommand{\HEADS}{\bullet^*h}
\newcommand{\TAILS}{\bullet^*t}

\begin{examples} \label{three}
  \itema Amy knows that it's tails and doesn't believe that it's heads and
  believes that Bob believes that it's heads.
\itemb \(
\begin{array}[t]{ll}
  \neg(\neg \TAILS + \Diamond_a \neg \TAILS) & \wedge \\
  \neg \neg \Diamond_a \neg \HEADS & \wedge \\
  \neg \Diamond_a \neg\neg\Diamond_b \neg \HEADS
\end{array}  
\)
\itemc \(\K_{a}\!\TAILS \; \wedge \, \neg\B_{a}\!\HEADS \; \wedge \; \B_{a}\B_{b}\HEADS\)
\itemd Bob believes that it's tails.
\iteme \(\B_{b} \TAILS \)
\end{examples}

% This conversion was done by hand. It would be good to put it into the scheme program.
% edge      : 695 Amy knows that its tails and doesnt believe that its heads and believes that Bob believes that its heads        (0 19)  t
%semantics : (((Not ((Not tails) + (Diamond amy (Not tails)))) & (Not (Not (Diamond amy (Not heads))))) & (Not (Diamond amy (Not (Not (Diamond bob (Not heads)))))))
% (((Not ((Not tails) + (Diamond amy (Not tails))))
% & (Not (Not (Diamond amy (Not heads)))))
% & (Not (Diamond amy (Not (Not (Diamond bob (Not heads)))))))
%\[
%\begin{array}{ll}
%  \neg(\neg \TAILS + \Diamond_a \neg \TAILS) & \wedge \\
%  \neg \neg \Diamond_a \neg \HEADS & \wedge \\
%  \neg \Diamond_a \neg\neg\Diamond_b \neg \HEADS
%\end{array}  
%\]

Sentence \exi{three}{d} is assigned a logical form that is syntactically
equivalent to \exi{three}{e}. Logical relations between propositions are checked in
the finite state calculus by checking set-theoretic relations between
sets of worlds.  Propositional entailment from $p$ to $q$ is decided
by checking in an interpreter for the finite state calculus whether $p
- q$ is non-empty.  In the model defined by Figure 2, proposition
\exi{three}{c} entails proposition \exi{three}{e}.

Another way of using the Fst interpreter is to display worlds in a given proposition.
\ex{p4worlds} shows the three words of length three in proposition \exi{three}{c}.
In the first one, Bob looks at heads, then Amy looks at heads, then Amy secretly
turns the coin, believing that she is turning it from heads to tails because she
believed after two steps that the coin was heads. Intuitively sentence
\exi{three}{a} is true in this scenario.

\begin{example} \label{p4worlds}
\(
\begin{array}[t]{l}  
1 0 \; bh \; 1 0 \; ah \; 1 0 \; aht \;  0 1 \\
1 0 \; bh \; 1 0 \; aht \; 0 1 \; at \; 0 1 \\
1 0 \; ah \; 1 0 \; bh \; 1 0 \; aht \; 0 1 \\
\end{array}
\)
\end{example}

\section{Discussion}
Epi\textsc{Kat} is designed for research in linguistic semantics, for
computational linguistics research on model-theoretically grounded semantics,
and for course modules on intensional formal semantics.
Currently, the grammar covers statives, {\em that-} and {\em
  whether}-complements, negation, and conjunction.
There are straightforward extensions to additional linguistic phenomena, such as
tense and perfective aspect \exi{extension}{a}, and the combination of
metaphysical modality and prospective aspect \exi{extension}{b}.

@@

%\clearpage
